

```{r libraries}
library(Seurat)
library(SeuratObject)
library(scales)
library(tidyverse)
library(sctransform)
library(RColorBrewer)
library(ggpubr)
library(colorspace)
```

##### Define names and paths
```{r paths}
dataset.name = "ALL.DF."
rawdatapath = "/path to raw file"
metadatapath = "/path to meta data"
plotspath = paste0("/path to plots")
Rfilespath = "/path to DF"
doubletspath = "/path to duplates"
setwd("/path to working directory")
mitoTH = 20
UMITH = 35000
```

##### Load the DF
```{r}
RBCpresentRBCplus <- Read10X(data.dir = rawdatapath)
```

##### Initialize the Seurat object
```{r}
RBCpresentRBCplusSeu <- CreateSeuratObject(counts = RBCpresentRBCplus,
                                           project = "pdr10X",
                                           min.cells = 3,
                                           min.features = 200,
                                           names.delim = "-",
                                           names.field = 2)
RBCpresentRBCplusSeu
rm(RBCpresentRBCplus)
table(RBCpresentRBCplusSeu@meta.data$orig.ident)
```

##### Add the patient clinical data
```{r}
Patient_metadata <- read.csv(paste0(metadatapath, "/Patient_metadata_coded.csv"), sep = ";", stringsAsFactors = FALSE,dec = ",")
names(Patient_metadata)[names(Patient_metadata) == "Patient_N"] <- "orig.ident"
Patient_metadata$orig.ident <- as.factor(Patient_metadata$orig.ident)
levels(Patient_metadata$orig.ident)
str(Patient_metadata)
metadata <- RBCpresentRBCplusSeu@meta.data
metadata$barcodes <- rownames(metadata)
str(metadata)
levels(metadata$orig.ident)
levels(Patient_metadata$orig.ident)

metadatatoadd <- dplyr::left_join(x = metadata, y = Patient_metadata, by = "orig.ident")
colnames(metadatatoadd)
rownames(metadatatoadd) <- metadatatoadd$barcodes

str(metadatatoadd)
Factor_columns <- c("Patient_ID", "orig.ident","Gender","Diabetes.Type","Hypertension","Smoking")
metadatatoadd[Factor_columns] <- lapply(metadatatoadd[Factor_columns], as.factor)  ## as.factor() could also be used
RBCpresentRBCplusSeu <- AddMetaData(RBCpresentRBCplusSeu,metadata = metadatatoadd) #add the metadata
```

##### Add patient colour palette to metadata
```{r}
PalettePatients = c("#006ba4","#ff800e","#ababab","#595959","#5f9ed1","#898989","#a2c8ec","#c85200","#ffbc79","#cfcfcf")
show_col(PalettePatients)

PatientLabels = data.frame("orig.ident" = c("1","2","3","4","5","6","7","8","9","10"),
                           "Colour_Patient" = PalettePatients, stringsAsFactors = FALSE)
str(PatientLabels)
show_col(PatientLabels$Colour_Patient)
metadata <- RBCpresentRBCplusSeu@meta.data
metadata$barcodes <- rownames(metadata)
metadatatoadd <- dplyr::left_join(x = metadata, y = PatientLabels, by = "orig.ident")
colnames(metadatatoadd)
rownames(metadatatoadd) <- metadatatoadd$barcodes
RBCpresentRBCplusSeu <- AddMetaData(RBCpresentRBCplusSeu,metadata = metadatatoadd["Colour_Patient"])
colnames(RBCpresentRBCplusSeu@meta.data)
str(RBCpresentRBCplusSeu@meta.data)
show_col(unique(RBCpresentRBCplusSeu@meta.data$Colour_Patient))
```

##### Reorder factors in the Seurat Object
```{r}
RBCpresentRBCplusSeu@meta.data$orig.ident <- factor(RBCpresentRBCplusSeu@meta.data$orig.ident, levels = c("1", "2", "3","4", "5", "6", "7",  "8", "9", "10"))

RBCpresentRBCplusSeu@meta.data$CME <- factor(RBCpresentRBCplusSeu@meta.data$CME, levels = c("No CME", "CME"))

RBCpresentRBCplusSeu@meta.data$Preoperative.laser <- factor(RBCpresentRBCplusSeu@meta.data$Preoperative.laser, levels = c(""))

RBCpresentRBCplusSeu@meta.data$PreVEGF <- factor(RBCpresentRBCplusSeu@meta.data$PreVEGF, levels = c("Untreated", "Treated"))

RBCpresentRBCplusSeu@meta.data$Statin.Therapy <- factor(RBCpresentRBCplusSeu@meta.data$Statin.Therapy, levels = c("Untreated", "Treated"))

```

##### PROCESSING MITOCHONDRIAL GENES
```{r}
RBCpresentRBCplusSeu[["percent.mt"]] <- PercentageFeatureSet(object = RBCpresentRBCplusSeu, pattern = "^MT-")
mt.genes <- rownames(RBCpresentRBCplusSeu)[grep("^MT-",rownames(RBCpresentRBCplusSeu))] # to extract the names of the mitochondrial genes
```

##### PROCESSING RIBOSOMAL GENES
```{r}
RBCpresentRBCplusSeu[["percent.ribo"]] <- PercentageFeatureSet(object = RBCpresentRBCplusSeu, pattern = "^RP[SL]") # this gives 178 genes - correct
ribo.genes <- rownames(RBCpresentRBCplusSeu)[grep("^RP[SL]",rownames(RBCpresentRBCplusSeu))] # to extract the names of the ribosomal genes
```

##### PROCESSING Mitochondrial filtering with Seurat
```{r}
selected.mt <- WhichCells(RBCpresentRBCplusSeu, expression = percent.mt < mitoTH)
length(selected.mt)
RBCpresentRBCplusSeu_filt <- subset(RBCpresentRBCplusSeu, cells = selected.mt)
RBCpresentRBCplusSeu_filt
table(RBCpresentRBCplusSeu_filt@meta.data$orig.ident)
```

##### PROCESSING UMI filtering with Seurat
```{r}
selected.UMI <- WhichCells(RBCpresentRBCplusSeu_filt, expression = nCount_RNA < UMITH)
length(selected.UMI)
RBCpresentRBCplusSeu_filt <- subset(RBCpresentRBCplusSeu_filt, cells = selected.UMI)
RBCpresentRBCplusSeu_filt
table(RBCpresentRBCplusSeu_filt@meta.data$orig.ident)
```

##### PROCESSING removing Doublets #####
```{r}
Pat1.RBC.present <- readRDS(paste0(doubletspath, "/Pat1.doublets.RBCpresent.rds"))
Pat2.RBC.present <- readRDS(paste0(doubletspath, "/Pat2.doublets.RBCpresent.rds"))
Pat3.RBC.present <- readRDS(paste0(doubletspath, "/Pat3.doublets.RBCpresent.rds"))
Pat4.RBC.present <- readRDS(paste0(doubletspath, "/Pat4.doublets.RBCpresent.rds"))
Pat5.RBC.present <- readRDS(paste0(doubletspath, "/Pat5.doublets.RBCpresent.rds"))
Pat6.RBC.present <- readRDS(paste0(doubletspath, "/Pat6.doublets.RBCpresent.rds"))
Pat7.RBC.present <- readRDS(paste0(doubletspath, "/Pat7.doublets.RBCpresent.rds"))
Pat8.RBC.present <- readRDS(paste0(doubletspath, "/Pat8.doublets.RBCpresent.rds"))
Pat9.RBC.present <- readRDS(paste0(doubletspath, "/Pat9.doublets.RBCpresent.rds"))
Pat10.RBC.present <- readRDS(paste0(doubletspath, "/Pat10.doublets.RBCpresent.rds"))

Pat1.RBC.removed <- readRDS(paste0(doubletspath, "/Pat1.doublets.RBCremoved.rds"))
Pat2.RBC.removed <- readRDS(paste0(doubletspath, "/Pat2.doublets.RBCremoved.rds"))
Pat3.RBC.removed <- readRDS(paste0(doubletspath, "/Pat3.doublets.RBCremoved.rds"))
Pat4.RBC.removed <- readRDS(paste0(doubletspath, "/Pat4.doublets.RBCremoved.rds"))
Pat5.RBC.removed <- readRDS(paste0(doubletspath, "/Pat5.doublets.RBCremoved.rds"))
Pat6.RBC.removed <- readRDS(paste0(doubletspath, "/Pat6.doublets.RBCremoved.rds"))
Pat7.RBC.removed <- readRDS(paste0(doubletspath, "/Pat7.doublets.RBCremoved.rds"))
Pat8.RBC.removed <- readRDS(paste0(doubletspath, "/Pat8.doublets.RBCremoved.rds"))
Pat9.RBC.removed <- readRDS(paste0(doubletspath, "/Pat9.doublets.RBCremoved.rds"))
Pat10.RBC.removed <- readRDS(paste0(doubletspath, "/Pat10.doublets.RBCremoved.rds"))

Joint.Doublets = unique(c(Pat1.RBC.present,Pat2.RBC.present,Pat3.RBC.present,Pat4.RBC.present,Pat5.RBC.present,
                          Pat6.RBC.present,Pat7.RBC.present,Pat8.RBC.present,Pat9.RBC.present,Pat10.RBC.present,
                          Pat1.RBC.removed,Pat2.RBC.removed,Pat3.RBC.removed,Pat4.RBC.removed,Pat5.RBC.removed,
                          Pat6.RBC.removed,Pat7.RBC.removed,Pat8.RBC.removed,Pat9.RBC.removed,Pat10.RBC.removed)) #530
selected.Doublets <- WhichCells(RBCpresentRBCplusSeu_filt, cells = Joint.Doublets, invert = TRUE)
length(selected.Doublets)
RBCpresentRBCplusSeu_filt <- subset(RBCpresentRBCplusSeu_filt, cells = selected.Doublets)
RBCpresentRBCplusSeu_filt
table(RBCpresentRBCplusSeu_filt@meta.data$orig.ident)
rm(RBCpresentRBCplusSeu)
```

# Median gene per cell and UMI per cell
```{r}
geneUMI = FetchData(object = RBCpresentRBCplusSeu_filt, vars = c("orig.ident", "nFeature_RNA", "nCount_RNA"))
geneUMI = geneUMI %>% 
  dplyr::group_by(orig.ident) %>% 
  dplyr::summarise_all(median) %>% 
  dplyr::mutate_if(is.double, as.integer)
write.csv(x = geneUMI, file = paste0(plotspath, "/", dataset.name, "metrics_per_patient.csv"))

geneUMI = FetchData(object = RBCpresentRBCplusSeu_filt, vars = c("nFeature_RNA", "nCount_RNA"))
geneUMI = geneUMI %>% 
  summarise_all(c(mean, min, max))
write.csv(x = geneUMI,file = paste0(plotspath, "/", dataset.name, "metrics_all.csv"))
```

##### PROCESSING CELL CYCLE GENES - POST FILTERING
```{r}
RBCpresentRBCplusSeu_filt <- CellCycleScoring(object = RBCpresentRBCplusSeu_filt,
                                         g2m.features = cc.genes.updated.2019$g2m.genes,
                                         s.features = cc.genes.updated.2019$s.genes)
RBCpresentRBCplusSeu_filt@meta.data$Phase = as.factor(RBCpresentRBCplusSeu_filt@meta.data$Phase)
```

##### PROCESSING - Calculate cell cycle difference
```{r}
RBCpresentRBCplusSeu_filt$CC.Difference <- RBCpresentRBCplusSeu_filt$S.Score - RBCpresentRBCplusSeu_filt$G2M.Score
```

##### PROCESSING - SCT for normalization, finding variable features and scaling
```{r}
RBCpresentRBCplusSeu_filtNoCC <- SCTransform(object = RBCpresentRBCplusSeu_filt,
                                        vars.to.regress = c("nCount_RNA", "CC.Difference", "percent.mt", "percent.ribo"),
                                        return.only.var.genes = FALSE,
                                        min_cells = 1, 
                                        method = "glmGamPoi")
rm(RBCpresentRBCplusSeu_filt)
```

##### Perform linear dimensional reduction
```{r}
RBCpresentRBCplusSeu_filtNoCCYesPCA <- RunPCA(object = RBCpresentRBCplusSeu_filtNoCC)
rm(RBCpresentRBCplusSeu_filtNoCC)
ALL.DF = RBCpresentRBCplusSeu_filtNoCCYesPCA
rm(RBCpresentRBCplusSeu_filtNoCCYesPCA)
VizDimLoadings(ALL.DF, dims = 1:2, reduction = "pca")
VariableFeaturePlot(ALL.DF)
top20NoRBC <- head(VariableFeatures(ALL.DF), 20)
plot1NoRBC <- VariableFeaturePlot(ALL.DF)
plot2NoRBC <- LabelPoints(plot = plot1NoRBC, points = top20NoRBC, repel = TRUE, xnudge = 0, ynudge = 0, max.overlaps = 20)
ggsave(plot = plot2NoRBC, paste0(dataset.name, "HVG.pdf"),device = cairo_pdf, width = 240, height = 180, units = "mm", 
       path = plotspath)
```

### Check cell-cycle genes
```{r}
## get PCA loadings
loadings <- as.data.frame(ALL.DF@reductions$pca@feature.loadings ) # with RunPCA with no RBC
# cc genes present in data
cc.genes.present <- rownames(loadings[rownames(loadings) %in% unlist(cc.genes.updated.2019),] ) # with RunPCA with no RBC
# put rownames to gene column
loadings$gene <- rownames(loadings)
# TRUE if a CC marker is present in the loadings
loadings$CC.genes <- loadings$gene %in% cc.genes.present
loadings[which(loadings$CC.genes == TRUE),'CC.genes.name'] <- loadings[which(loadings$CC.genes == TRUE),'gene']
loadings$CC.genes.name
# Plot a component to see the CC genes
ggplot(loadings, aes(x=PC_1,y=gene, color=CC.genes) ) + 
  geom_point(alpha=0.5)+geom_label(aes(label=CC.genes.name))+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
# Take only 30 PCs
lod.rnk <- loadings[,c(1:30)]
lod.rnk$gene = rownames(lod.rnk) 
lod.rnk <- lod.rnk[,1:30]
# Check the rank of CC genes in each PCs
dir <- "pos"
df = apply(lod.rnk, 2, FUN=function(x){
  
  if(dir == "pos"){
    pos <- x[x>=0]
    pos <- pos[order(pos, decreasing = TRUE)]
    which( names(pos) %in% cc.genes.present )
  }else{
    neg <- x[x<0]
    neg <- neg[order(neg)]
    which( names(neg) %in% cc.genes.present )}}) 
df = plyr::ldply(df, rbind)
write.csv(x = df,file = paste0(plotspath, "/", dataset.name, "PC_ranking_CCgenes.csv") )
# Cell cycle genes are ranking high!
```

##### Determine the 'dimensionality' of the ALL.DF
```{r}
ElbowPlot(object = ALL.DF, ndims = 50)
```

##### Select how many PCs
```{r}
# Determine percent of variation associated with each PC
pct = data.frame("PC" = colnames(ALL.DF@reductions$pca),
                 "rank" = c(1:50),
                 "percent.stdev" = ALL.DF@reductions$pca@stdev / sum(ALL.DF@reductions$pca@stdev) * 100)

# Calculate cumulative percents for each PC
pct$cumu <- cumsum(pct$percent.stdev)

# Determine which PC exhibits cumulative percent greater than 90% and % variation associated with the PC as less than 5
PC_criteria1 = pct[pct$cumu > 90 & pct$percent.stdev < 5, "rank"][1]
PC_criteria1

# Determine the difference between variation of PC and subsequent PC
str(pct)
PC_criteria2 = pct %>% 
  mutate(diff_stdev = percent.stdev - lag(percent.stdev)) %>% 
  arrange(diff_stdev) %>% 
  filter(abs(diff_stdev) > 0.1) %>% 
  arrange(-rank)
PC_criteria2 = PC_criteria2[1, "rank"]

# Minimum of the two calculation
pcs <- min(PC_criteria1, PC_criteria2)

pcs

# Elbow plot to visualize 
Elbow = ggplot(pct, aes(cumu, percent.stdev, label = rank, color = rank > pcs)) + 
  geom_text() + 
  geom_vline(xintercept = 90, color = "grey") + 
  geom_hline(yintercept = min(pct$percent.stdev[pct$percent.stdev > 5]), color = "grey") +
  theme_bw()

ggsave(plot = Elbow, paste0(dataset.name, "ElbowPlot.QuantitativeApproach", ".pdf"),device = cairo_pdf, width = 240, height = 180, units = "mm", 
       path = plotspath)
```

##### Cluster the cells
```{r}
ALL.DF <- FindNeighbors(object = ALL.DF, dims = 1:pcs)
ALL.DF <- FindClusters(object = ALL.DF, resolution = c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0, 1.1, 1.2,1.3,1.4,1.5,1.6,1.7,1.8,1.9,2.0))

# Clusters vs resolution
clustersRBCplus <- sapply(grep("^SCT_snn_res",colnames(ALL.DF@meta.data),value = TRUE),
                           function(x) length(unique(ALL.DF@meta.data[,x])))
clustersRBCplus
``` 

##### UMAP
```{r}
set.seed(1234)
ALL.DF <- RunUMAP(object = ALL.DF, dims = 1:pcs, n.components = 2)
```

##### TSNE
```{r}
set.seed(1234)
ALL.DF <- RunTSNE(object = ALL.DF, reduction = "pca", dims = 1:pcs, dim.embed = 2)
```

##### Define clusters
```{r}
df_names <- ALL.DF@meta.data[c("SCT_snn_res.0.2", "SCT_snn_res.0.3")]
df_names$ClusterName <- NA
df_names$ClusterName[df_names$SCT_snn_res.0.2 == 0] <- "T_NK"
df_names$ClusterName[df_names$SCT_snn_res.0.2 == 1] <- "PC_SMC"
df_names$ClusterName[df_names$SCT_snn_res.0.2 == 2] <- "EC"
df_names$ClusterName[df_names$SCT_snn_res.0.2 == 3] <- "MO_MP_MiG"
df_names$ClusterName[df_names$SCT_snn_res.0.2 == 4] <- "EC"
df_names$ClusterName[df_names$SCT_snn_res.0.2 == 5] <- "EC"
df_names$ClusterName[df_names$SCT_snn_res.0.2 == 6] <- "FB"
df_names$ClusterName[df_names$SCT_snn_res.0.2 == 7] <- "M端G"
df_names$ClusterName[df_names$SCT_snn_res.0.2 == 8] <- "B"
df_names$ClusterName[df_names$SCT_snn_res.0.2 == 9] <- "PC_SMC"
df_names$ClusterName[df_names$SCT_snn_res.0.2 == 10] <- "MC"
df_names$ClusterName[df_names$SCT_snn_res.0.2 == 11] <- "NP"
df_names$ClusterName[df_names$SCT_snn_res.0.2 == 12] <- "Plasma"
unique(df_names$ClusterName)
metadata <- as.data.frame(df_names["ClusterName"])
ALL.DF <- AddMetaData(ALL.DF,metadata = metadata,col.name = "ClusterNames")
unique(ALL.DF@meta.data$ClusterNames)
```

##### Add Cluster colours to metadata #####
```{r}
metadata <- ALL.DF@meta.data
metadata$barcodes <- rownames(metadata)
levels(metadata$ClusterNames)
metadata <- metadata[,c("ClusterNames", "barcodes")]
metadatatoadd <- dplyr::left_join(x = ALL.DF.CellLabels[,c("ClusterNames", "ClusterNamesColours")], y = metadata, by = "ClusterNames")

rownames(metadatatoadd) <- metadatatoadd$barcodes
str(metadatatoadd)
show_col(unique(metadatatoadd$ClusterNamesColours))
metadatatoadd <- metadatatoadd["ClusterNamesColours"]
ALL.DF <- AddMetaData(ALL.DF,metadata = metadatatoadd)
show_col(unique(as.character(ALL.DF$ClusterNamesColours)))
```

##### Save the R object! #####

```{r}
saveRDS(ALL.DF, file = paste0(Rfilespath, "/", dataset.name, "rds"))
```
##### END ####

```

##### Save the R object! #####
```{r}
saveRDS(ALL.DF, file = paste0(Rfilespath, "/", dataset.name, "rds"))
```
```

##### Define clusters for CellChat
```{r}
dataset.name = "ALL.DF.subset."
EC.clusters = EC.DF@meta.data["ClusterNames"]
PC.clusters = PC.SMC.FB.DF@meta.data["ClusterNames"]
L.clusters = Lymphoid.DF.subset@meta.data["ClusterNames"]
M.clusters = Myeloid.DF.subset@meta.data["ClusterNames"]
Mug.clusters = ALL.DF.subset@meta.data["ClusterNames"]
Mug.clusters$Cell = rownames(Mug.clusters)
Mug.clusters = Mug.clusters[Mug.clusters$ClusterNames == "M端G",]
Mug.clusters = Mug.clusters["ClusterNames"]

sum(nrow(EC.clusters), nrow(PC.clusters),nrow(L.clusters), nrow(M.clusters), nrow(Mug.clusters))

Joint = bind_rows(EC.clusters, PC.clusters, L.clusters, M.clusters, Mug.clusters)
unique(Joint$ClusterNames)
levels(Joint$ClusterNames)
ALL.DF.subset <- AddMetaData(ALL.DF.subset, metadata = Joint, col.name = "ClusterNamesJoint")
unique(levels(ALL.DF.subset@meta.data$ClusterNamesJoint))
unique(ALL.DF.subset@meta.data$ClusterNamesJoint)
```

##### Reorder factors in the Seurat Object
```{r}
ALL.DF.subset@meta.data$ClusterNamesJoint <- factor(ALL.DF.subset@meta.data$ClusterNamesJoint,
                                             levels = c("Damaged_EC","Stressed_EC","PLCG2hi_EC","FABP5hi_EC","Immune_EC","EndMT_EC","Venous_EC","Tip_EC",
                                                        "Damaged_PC","GRPhigh_PC","MMP9high_PC","Prolif._PC","PLNhigh_SMC","ACANhigh_SMC","RGS5high_SMC","MyoFB","FB",
                                                        "M端G",
                                                        "CD4.naive","CD4.TRM","Th1","Treg","CD8.TRM","CD8.MT","CD8.CTL","GD","Prolif.T","NKT","NK","B","Plasma",
                                                        "Preactiv.MG","Preactiv.MG.IFNG","Activ.MG","AntiInfl.MG","TAGLN.MP","M1.MP","Periv.MP","MC","NP","cDC2"))
ALL.DF.subset@meta.data$ClusterNamesJoint
unique(levels(ALL.DF.subset@meta.data$ClusterNamesJoint))
unique(ALL.DF.subset@meta.data$ClusterNamesJoint)
```

##### Remove filtered cell clusters
```{r}
Idents(object = ALL.DF.subset) <- "ClusterNamesJoint" 
levels(ALL.DF.subset)

ALL.DF.subset <- subset(ALL.DF, cells = rownames(ALL.DF@meta.data[!ALL.DF@meta.data$ClusterNamesJoint %in% c("RBC", "MSC.like", "EC.MG"),]))

ALL.DF.subset$ClusterNamesJoint = droplevels(ALL.DF.subset$ClusterNamesJoint)

levels(ALL.DF.subset@meta.data$ClusterNamesJoint)
```

##### Add Cluster colours to metadata #####
```{r}
metadata <- ALL.DF.subset@meta.data
metadata$barcodes <- rownames(metadata)
levels(metadata$ClusterNamesJoint)
metadata <- metadata[,c("ClusterNamesJoint", "barcodes")]
metadatatoadd <- dplyr::left_join(x = ALL.DF.subset.CellLabelsJoint[,c("ClusterNamesJoint", "ClusterNamesJointColours")], y = metadata, by = "ClusterNamesJoint")

rownames(metadatatoadd) <- metadatatoadd$barcodes
str(metadatatoadd)
show_col(unique(metadatatoadd$ClusterNamesJointColours))
metadatatoadd <- metadatatoadd["ClusterNamesJointColours"]
ALL.DF.subset <- AddMetaData(ALL.DF.subset,metadata = metadatatoadd)
show_col(unique(as.character(ALL.DF.subset$ClusterNamesJointColours)))
```

##### Save the R object! #####
```{r}
saveRDS(ALL.DF.subset, file = paste0(Rfilespath, "/", dataset.name, "rds"))
```






##### Rename the MO/MP/MiG cluster
```{r}
unique(ALL.DF@meta.data$ClusterNames)
levels(ALL.DF@meta.data$ClusterNames)
ALL.DF@meta.data$ClusterNames = factor(ALL.DF@meta.data$ClusterNames,
                                       levels = c(levels(ALL.DF@meta.data$ClusterNames), "MP_MG"))

ALL.DF@meta.data[ALL.DF@meta.data$ClusterNames == "MO_MP_MiG","ClusterNames"] = "MP_MG"
ALL.DF@meta.data$ClusterNames = droplevels(ALL.DF@meta.data$ClusterNames)
table(is.na(ALL.DF@meta.data$ClusterNames))
ALL.DF@meta.data$ClusterNames = factor(ALL.DF@meta.data$ClusterNames,
                                       levels = c("EC","PC_SMC","FB","M端G","MP_MG", "MC","NP","T_NK","B","Plasma"))
unique(ALL.DF@meta.data$ClusterNames)
levels(ALL.DF@meta.data$ClusterNames)

```

##### Save the R object! #####
```{r}
saveRDS(ALL.DF, file = paste0(Rfilespath, "/", dataset.name, "rds"))
```

